############ EVERYTHING NEEDS TO BE COPY PASTED OUT OF THIS CURSED R MARKDOWN FILE BECAUSE THE IMAGES SUCK!############ 


---
title: "Study Room Data - Library"
author: "Ryan Iacovone"
date: "12/10/2022"
output: word_document
editor_options: 
  chunk_output_type: inline
---

```{r set_options, message=FALSE, include=FALSE, paged.print=FALSE}
#Loading in all appropriate libraries for the report 
library(tidyverse)
library(janitor) # the tabyl function 
library(scales) #functions for creating breaks and labels for axes and color scales
library(ggthemes)
library(readxl)
library(stringr) # manipulating strings
source("http://pcwww.liv.ac.uk/~william/R/crosstab.r") #Library for crosstab function
library(expss) # Creating tables 
library(writexl)
library(RColorBrewer)
library(lubridate) #Formatting dates and times

#Code to knit the file even if there are errors 
knitr::opts_chunk$set(error = TRUE)
```


#Data Wrangling 
```{r include=FALSE}
#Loading in the excel file omitting all missing values 

study <- read_excel("Data/Example Data.xlsx") %>%
  na.omit()

#Using the factor() function to chagne the varaibles Time and Room_Avaliable from their default character variables into factor varaibles. I specifiy the levels of each factor to ensure the proper order for the graph legends later on
#Encoding the variable Time as a factor with three levels "M", "A", "E" soon to represent "morning" "afternoon" and "evening 
study$Time <- factor(study$Time, levels = c("M", "A", "E"))

study$Room_Avaliable <- factor(study$Room_Avaliable, levels = c("yes", "no"))

#Getting a brief look at our data set to make sure it looks good 
head(study)

#Applying labels to the factors of variable time to be applied later on in the tabyl() to create our cross tab  
study1 = apply_labels(study, 
                     Time = c("Afternoon" = "A",
                              "Evening" = "E",
                              "Morning" = "M"))
```


```{r echo=FALSE}
#Function from the stringr library that will count all instances of 'yes' and 'no' observations from the variable Room_Avaliable 
y <-str_count(study$Room_Avaliable, "yes")
n <-str_count(study$Room_Avaliable, "no")

#Using the summarize function to create a data frame that highlights some important summary statistics to be included in the report  
m <-study %>%
  summarise(yes = sum(y), no = sum(n), total = yes+no, Success_Rate = yes/total,
            min = min(Numer_Of_People),
            max = max(Numer_Of_People),
            MeanG = mean(Numer_Of_People),
            MeanC = (total/18),
            sd = sd(Numer_Of_People),
            Median = median(Numer_Of_People)) 
print(m)

summary(study$Numer_Of_People)
```


#Cross tabulation illustrating the success rate of patrons getting a study room by the time of day
```{r echo=FALSE}
#this code is creating a cross-tabulation table from the study1 data frame and adding row and column totals, as well as a new column with the success rate calculated from the yes and Total columns. The success rate column is also formatted as a percentage.

tab <- tabyl(study1, Time, Room_Avaliable) %>%
  adorn_totals(c("row", "col")) %>%
  mutate(Success_rate = yes/Total) %>%
  adorn_pct_formatting(,,,Success_rate)

print(tab)
```


#Cross tabulation investigating success rate of getting a study by individual day 
```{r echo=FALSE}
# The as.Date() function is used to convert the orginal character date column into a date vector. It takes a character vector as input and returns a date vector with the same length. 
study$newdate <- as.Date(study$Date)

#Formats new date function into the format 11/07/2022 (month, day, 4 digit year)
study$newdate <- format(study$newdate, "%m/%d/%Y")

study <- study %>% mutate(days = weekdays(Date))


tab <- tabyl(study, newdate, Room_Avaliable, days) %>%
  adorn_totals(c("row", "col")) %>%
  mutate(Success_rate = yes/Total) %>%
  adorn_pct_formatting(,,,Success_rate) 
 
print(tab)

#Desired output 

#      Time yes no Total Success_rate
# Afternoon  82 42   124        66.1%
#   Evening  14  3    17        82.4%
#   Morning  61 11    72        84.7%
#     Total 157 56   213        73.7%
```


#Boxplot 
```{r}
study %>% 
  ggplot(aes(x = Numer_Of_People)) + 
  geom_boxplot()
```


#Pie plot showing patron requests for study room based on the size of their group
```{r}
# Calculate percentages
totals <- study %>% count(Numer_Of_People)

totals$percent_NOP <- totals$n / sum(totals$n) * 100

totals$Numer_Of_People <- as.character(totals$Numer_Of_People)

# Create the pie chart
ggplot(totals, aes(x = "", y = percent_NOP, fill = Numer_Of_People)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar(theta = "y") +
  geom_text(aes(label = paste0(round(percent_NOP), "%")), 
            position = position_jitterdodge(jitter.width = 0.2, dodge.width = .8), 
            size = 4) +
  #geom_text(aes(label = paste0(round(percent_NOP), "%")), position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette = "Dark2", name = "Number of People per Group") +
  labs(
    title = "Study Rooms Requests by Group Size"
  ) +
  theme_void()
```



#Below is a data visualization (histogram) showing patron requests for study room based on the size of their group
```{r echo=FALSE}
size <- study %>% 
  ggplot(aes(x = Numer_Of_People)) + 
  geom_histogram(stat = "count", position = "dodge2", color = "black", fill = "#1F78B4", width = .6) +
  ggtitle("Study Rooms Requests by Group Size") +
  xlab("Group Size (Number of People per Group)") +
  ylab("Observations") +
  labs(caption = "Figure 1.1")  +
  scale_y_continuous(
    breaks = seq(0, 190, by = 10),
    limits = c(0, 190)) +
  theme_clean() +
  theme(legend.position = c(0.6, 0.6),
        legend.direction = "horizontal",
        legend.title = element_text(size = 10.5), 
        legend.text = element_text(size = 10))
size
```


#Below is a data visualization (histogram) showing whether a patron was able to get study based on the size of their group
```{r echo=FALSE}
success <- study %>% ggplot(aes(x=Numer_Of_People, fill = Room_Avaliable)) + 
  geom_histogram(stat= "count" , position = "dodge2", color="black") +
  xlab('Group Size (Number of People per Group)') +
  ylab("Observations") +
  ggtitle("Success of Getting a Study Room by Group Size") +
  labs(caption = "Figure 1.2") +
  scale_fill_manual(name= "Room Available?", labels= c("Yes", "No"), values=c("#66A61E", "#7570B3")) +
  scale_y_continuous(
    breaks = seq(0, 145, by = 10)) + 
  theme_clean() +
  theme(legend.position = c(.7, .6), 
        plot.title = element_text(size = 12)) 

success
```


#Below we see a data visualization (histogram) illustrating study room requests by the time of day. 
```{r echo=FALSE}
time <- study %>% ggplot(aes(x=Numer_Of_People, fill = Time)) + 
  geom_histogram(stat= "count" , position = "dodge2", color="black") +
  xlab("Group Size (Number of People per Group)") +
  ylab("Observaitons") +
  ggtitle("Study Rooms Requests by Time") +
  labs(caption = "Figure 1.3")+
  scale_fill_brewer(labels= c("Morning", "Afternoon", "Evening"), palette = "Dark2") +
  scale_y_continuous(
    breaks = seq(0, 110, by = 5),
    limits = c(0, 105)) +
  theme_clean() +
  theme(legend.position = c(.6, .6),
        legend.direction = "horizontal",
        legend.title = element_text(size = 10.5), 
        legend.text = element_text(size = 10))

time

#ggsave(one, file = "C:/Users/Ryan/Coding Projects/KDL Project/Quarterly Reports/Graphs/testingsy.png")
```




```{r eval=FALSE, include=FALSE}
###############NEED TO GO THROUGH AND RE COPY ALL GRAPHS INTO WORD DOC ###############
#ggsave(one, file = "C:/Users/Ryan/Coding Projects/KDL Project/Quarterly Reports/Graphs/visitorsweeklarge.png")


#Code to export table to an excel sheet!

#write_xlsx(tab, "C:/Users/Ryan/Coding Projects/KDL Project/Study Rooms/Figs/Hi.xlsx")



#Displays all colorblind friendly colors in brewer library
display.brewer.all(colorblindFriendly = TRUE)   

#Finding and then displaying the code names for specific colorblind friendly colors to use in the following data visualizations 
display.brewer.pal(8, "Paired")
brewer.pal(8, "Paired")
```