```{r}
#taking in all the libraries and data wrangling from this initial R file 
source("C:/Users/Ryan/Coding Projects/Public Forks/Study Rooms pub/Wrangling.R")
```

#boxplot 
```{r}
study %>% 
  ggplot(aes(x = Numer_Of_People)) + 
  geom_boxplot()
```


#Pie plot showing patron requests for study room based on the size of their group
```{r}
# Calculate percentages
totals <- study %>% count(Numer_Of_People)

totals$percent_NOP <- totals$n / sum(totals$n) * 100

totals$Numer_Of_People <- as.character(totals$Numer_Of_People)

# Create the pie chart
ggplot(totals, aes(x = "", y = percent_NOP, fill = Numer_Of_People)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar(theta = "y") +
  geom_text(aes(label = paste0(round(percent_NOP), "%")), 
            position = position_jitterdodge(jitter.width = 0.2, dodge.width = .8), 
            size = 4) +
  #geom_text(aes(label = paste0(round(percent_NOP), "%")), position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette = "Dark2", name = "Number of People per Group") +
  labs(
    title = "Study Rooms Requests by Group Size"
  ) +
  theme_void()
```


#Below is a data visualization (histogram) showing patron requests for study room based on the size of their group
```{r}
size <- study %>% 
  ggplot(aes(x = Numer_Of_People)) + 
  
  geom_histogram(stat = "count", position = "dodge2", color = "black", fill = "#1F78B4", width = .6) +
  
  ggtitle("Study Rooms Requests by Group Size") +
  xlab("Group Size (Number of People per Group)") +
  ylab("Observations") +
  labs(caption = "Figure 1.1")  +
  
  scale_y_continuous(
    breaks = seq(0, 190, by = 10),
    limits = c(0, 190)) +
  
  theme_clean() +
  
  theme(legend.position = c(0.6, 0.6),
        legend.direction = "horizontal",
        legend.title = element_text(size = 10.5), 
        legend.text = element_text(size = 10))

size
```


#Below is a data visualization (histogram) showing whether a patron was able to get study based on the size of their group
```{r}
success <- study %>% ggplot(aes(x=Numer_Of_People, fill = Room_Avaliable)) + 
  
  geom_histogram(stat= "count" , position = "dodge2", color="black") +
  
  xlab('Group Size (Number of People per Group)') +
  ylab("Observations") +
  ggtitle("Success of Getting a Study Room by Group Size") +
  labs(caption = "Figure 1.2") +
  
  scale_fill_manual(name= "Room Available?", labels= c("Yes", "No"), values=c("#66A61E", "#7570B3")) +
  
  scale_y_continuous(
    breaks = seq(0, 145, by = 10)) + 
  theme_clean() +
  
  theme(legend.position = c(.7, .6), 
        plot.title = element_text(size = 12)) 

success
```


#Below we see a data visualization (histogram) illustrating study room requests by the time of day. 
```{r}
time <- study %>% ggplot(aes(x=Numer_Of_People, fill = Time)) + 
  
  geom_histogram(stat= "count" , position = "dodge2", color="black") +
  
  xlab("Group Size (Number of People per Group)") +
  ylab("Observaitons") +
  ggtitle("Study Rooms Requests by Time") +
  labs(caption = "Figure 1.3")+
  
  scale_fill_brewer(labels= c("Morning", "Afternoon", "Evening"), palette = "Dark2") +
  
  scale_y_continuous(
    breaks = seq(0, 110, by = 5),
    limits = c(0, 105)) +
  
  theme_clean() +
  
  theme(legend.position = c(.6, .6),
        legend.direction = "horizontal",
        legend.title = element_text(size = 10.5), 
        legend.text = element_text(size = 10))

time
```




```{r eval=FALSE, include=FALSE}
#The elements in the list do not have any names associated with them. When you use the names function on this list, it returns NULL.

#To create a named list, you have to specify the names of the elements when creating the list, like this: 
plots <- list(size = size, success = success, time = time)

plots_names <- names(plots)


# Save each plot to a file using the names of each plot in addition to their index to itterate over it 
for (plot in seq_along(plots)) {
  ggsave(filename = paste0(plots_names[[plot]], ".png"), plot = plots[[plot]], path = "C:/Users/Ryan/Coding Projects/Public Forks/Study Rooms pub/Figs")
}
```


```{r}
#Displays all colorblind friendly colors in brewer library
display.brewer.all(colorblindFriendly = TRUE)   

#Finding and then displaying the code names for specific colorblind friendly colors to use in the following data visualizations 
display.brewer.pal(8, "Paired")
brewer.pal(8, "Paired")
```